New Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2024-09-24 jso.qmd
change D -> R in proposition 1

\begin{prop}\label{prop:convex-concave}
Let $g_1$ be a convex, strictly decreasing function and $g_2$ be a concave, strictly decreasing function, both defined on $[0, D]$ where $D>0$, and taking values in $[0, 1]$. Then
$$\varsigma(g_1) < \varsigma(g_2)$$
\end{prop}

\begin{proof}
Let $r_1 := \underset{r}{\arg \min }\,g_1'(r)$ and $r_2 := \underset{r}{\arg \min }\,g_2'(r)$.
Since $g_1$ is convex, $g_1''(r) >= 0 \; \forall r \in [0, D]$, meaning that $g_1'$ is an increasing function, taking its minimum for $r_1=0$. As a result, $\varsigma(g_1)=-4 \times g'(0) \times 0 =0$.
Since $g_2$ is concave, $g_2''(r) <= 0 \; \forall r \in [0, D]$, meaning that $g_2'$ is a decreasing function, taking its minimum for $r_2=D>0$. Since $g_2$ is strictly decreasing, $g_2'(r) < 0 \; \forall r \in [0, D]$. In particular $g_2'(D)<0$. As a result $\varsigma(g_2)=-4 \times g'(D) \times D >0$. This proves that $\varsigma(g_1) < \varsigma(g_2)$.
\end{proof}

>>>>

\begin{prop}\label{prop:convex-concave}
Let $g_1$ be a convex, strictly decreasing function and $g_2$ be a concave, strictly decreasing function, both defined on $[0, R]$ where $R>0$, and taking values in $[0, 1]$. Then
$$\varsigma(g_1) < \varsigma(g_2)$$
\end{prop}

\begin{proof}
Let $r_1 := \underset{r}{\arg \min }\,g_1'(r)$ and $r_2 := \underset{r}{\arg \min }\,g_2'(r)$.
Since $g_1$ is convex, $g_1''(r) \geq 0 \; \forall r \in [0, R]$, meaning that $g_1'$ is an increasing function, taking its minimum for $r_1=0$. As a result, $\varsigma(g_1)=-4 \times g'(0) \times 0 =0$.
Since $g_2$ is concave, $g_2''(r) \leq 0 \; \forall r \in [0, R]$, meaning that $g_2'$ is a decreasing function, taking its minimum for $r_2=D>0$. Since $g_2$ is strictly decreasing, $g_2'(r) < 0 \; \forall r \in [0, R]$. In particular $g_2'(R)<0$. As a result $\varsigma(g_2)=-4 \times g'(R) \times R >0$. This proves that $\varsigma(g_1) < \varsigma(g_2)$.
\end{proof}

### 2024-09-24 jso.tex
change D -> R in proposition 1

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, opacitybacktitle=0.6, breakable, coltitle=black, titlerule=0mm, bottomrule=.15mm, arc=.35mm, rightrule=.15mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, colback=white, colbacktitle=quarto-callout-note-color!10!white, opacityback=0, title={Algorithm: Jellyfish Optimizer Pseudo Code}, bottomtitle=1mm, left=2mm, toptitle=1mm]

>>>>

\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, breakable, bottomtitle=1mm, colframe=quarto-callout-note-color-frame, titlerule=0mm, toprule=.15mm, left=2mm, opacitybacktitle=0.6, colbacktitle=quarto-callout-note-color!10!white, rightrule=.15mm, colback=white, leftrule=.75mm, toptitle=1mm, opacityback=0, title={Algorithm: Jellyfish Optimizer Pseudo Code}, arc=.35mm, coltitle=black]
